---
title: "Assignment 1"
format: html
editor: visual
---

---
title: "Assignment 1"
author: "Özgenur Şensoy"
date: "2022-10-01"
---

# \| About Me

[Hello folks!]{style="font-size: 20px;"}

I'm Özgenur Şensoy, MSc in Big Data Analytics. I graduated from MEF University from the Department of Elementary Mathematics Education. Since I did not feel like I belonged there during my internships, I switched to data analytics where I could be more productive. I want to put my data science skills into practice in a few companies that I dream of. In addition, I want to progress by nourishing my knowledge with courses on artificial intelligence.

[![LinkedIn Badge](https://img.shields.io/badge/linkedin-%230077B5.svg?&style=for-the-badge&logo=linkedin&logoColor=white&color=071A2C)](https://www.linkedin.com/in/özgenurşensoy/)

# \| Yotube Video

### Data Visualization

<iframe width="560" height="315" src="https://www.youtube.com/embed/5zJC0AB-UK8?si=wTYh_CmeJ242Af2M" title="YouTube video player" frameborder="0" allow="accelerometer; autoplay; clipboard-write; encrypted-media; gyroscope; picture-in-picture; web-share" allowfullscreen>

</iframe>

</iframe>

[*Teaching R online with RStudio Cloud*](https://www.youtube.com/watch?v=5zJC0AB-UK8&list=PL9HYL-VRX0oTOK4cpbCbRk15K2roEgzVW&index=21)

I chose to watch the video titled **"Data visualization and plotting with Shiny for Python \|\| Carson Sievert \|\| RStudio"** The video covers how to create interactive data visualization using Shiny, Python, and Pandas. Here are the key topics:

**Layout and Slider:** At the beginning of the video, we learn how to lay out a user interface and add interactive elements such as sliders using Shiny. This allows users to interact with data or graphs.

**Reactive Calculations :**The term "Reactive calculations" refers to the ability of users to make calculations based on data. For example, you can create a structure where the calculations are automatically updated when a user changes the slider.

**Render Plot:** Specifies how to render and update graphics or plots to be displayed to the user. Data-driven charts can refresh automatically as users interact.

**Pandas Plotting:** Pandas is a widely used library for data analysis and manipulation in Python. The video could possibly also cover how to analyze data using DataFrames and how to use Pandas' plotting capabilities.

The video explains how you can create an app with an interactive graphic. This implementation seems to change the number of bars in the calculated histogram when you change a slider. The video shows you how to layout such interactive applications using "layout sidebar", a subpackage of Shiny. This allows users to make the data and chart more interactive. Additionally, "reactive calculations" and "render plot" topics are also discussed in the video. "Reactive calculations" appears to be a feature that defines how calculations can be performed based on input values. "Render plot" explains how to create and display graphics. This shows how you can create different types of plots interactively using plot libraries such as Matplotlib. The video also provides examples using different graphics packages, for example showing how packages such as Seaborn, Plotnine, Pandas, Hollowvies, xarray and geopandas can be used. It looks like this video might offer useful information to those interested in data visualization using Shiny and Python.

------------------------------------------------------------------------
# \| Three R Posts


### 1- Mastering Data Visualization in R
This R data visualization guide provides an overview of the various techniques, libraries, and best practices for creating visually stunning visuals that effectively communicate your data insights. You will be better equipped to explore, analyze, and present your data findings in a compelling and engaging manner if you master data visualization in R. Whether you're a seasoned data analyst or just starting out, the world of data visualization in R offers limitless opportunities to maximize the value of your data.

[*Post Link*](https://medium.com/@HalderNilimesh/mastering-data-visualization-in-r-a-comprehensive-guide-to-creating-stunning-visuals-and-f733564a8a41)


### 2- Human Resources Analytics: Exploring Employee Data in R
The focus of this is on analyzing recruiting data, particularly in the context of the sales department and the various recruiting channels from which employees were hired. The R code includes loading the dataset, providing an overview of the data, and identifying the recruiting sources used by the company. Attrition rates, or the frequency of employees leaving the company, are also examined by recruiting sources, allowing for the identification of channels with both high and low attrition rates. Data visualizations in the form of bar charts are used to present the results, making it easier to compare and interpret the findings.

Sales numbers by recruiting source Which recruiting channel produces the best salespeople? One quality of hire metric you can use is sales quota attainment, or how much a salesperson sold last year relative to their quota. An employee whose sales_quota_pct equals .75 sold 75% of their quota, for example. This metric can be helpful because raw sales numbers are not always comparable between employees.

Calculate the average sales quota attainment achieved by hires from each recruiting source.

```{r}
# Find the average sales quota attainment for each recruiting source
avg_sales <- recruitment %>%
  group_by(recruiting_source) %>% 
  summarize(avg_sales_quota_pct = mean(sales_quota_pct)) 
  
# Display the result
avg_sales

```

[*For More*](https://rpubs.com/alifrady/HR_analysis)


### 3- Default Parameter Value
The following example shows how to use a default parameter value.

If we call the function without an argument, it uses the default value:
```{r}
Example
my_function <- function(country = "Norway") {
  paste("I am from", country)
}

my_function("Sweden")
my_function("India")
my_function() # will get the default value, which is Norway
my_function("USA")
```

[*For More*](https://www.w3schools.com/r/r_functions.asp)
